---
title: "Project"
author: "Group"
date: "18/11/2021"
output: html_document
---

#Asteroids Potential Hazards Prediction

This markdown file contains various data preparation and analysis techniques learned during the course to predict if an Asteroid is a potential hazard or not.


#DATA

First we start of by inputting the data we will be using for our prediction.
The used used is from kaggle: https://www.kaggle.com/sakhawat18/asteroid-dataset

#Features of the Data set

1. SPK-ID: Object primary SPK-ID
2. Object ID: Object internal database ID
3. Object fullname: Object full name/designation
4. pdes: Object primary designation
5. name: Object IAU name
6. NEO: Near-Earth Object (NEO) flag
8. H: Absolute magnitude parameter
9. Diameter: object diameter (from equivalent sphere) km Unit
10. Albedo: Geometric albedo
11. Diameter_sigma: 1-sigma uncertainty in object diameter km Unit
12. Orbit_id: Orbit solution ID
13. Epoch: Epoch of osculation in modified Julian day form
14. Equinox: Equinox of reference frame
15. e: Eccentricity
16. a: Semi-major axis au Unit
17. q: perihelion distance au Unit
18. i: inclination; angle with respect to x-y ecliptic plane
19. tp: Time of perihelion passage TDB Unit
20. moid_ld: Earth Minimum Orbit Intersection Distance au Unit

The above are the features of perticular asteroid given in the dataset.

Our goal to predict: PHA: Potentially Hazardous Asteroid (PHA) flag


#Libararies:

```{r}
library(readr)
library(ggplot2)
```

##Data preprocessing:

Inputting the dataset

```{r}
dataset <- read_csv("Desktop/DPA Project/dataset.csv")
#View(dataset)
#summary(dataset)
df<-data.frame(dataset)
summary(df)
head(df)
#View(df)
```

Finding if there are null values:

```{r}
colSums(is.na(df))
```
From above we can see that there are 'NA' values present in the dataset which need to be taken care of before we proceed to create our model.


#Data Cleaning

From our dataset we remove the columns 'id' and 'columns' as they are not required and are redundant information for our model.

Since are dataset is big we will omit the values containing 'NA' instead of replacing them.

```{r}
ds <- df[-c(1, 6)]
ds<-na.omit(ds)
colSums(is.na(ds))
#View(ds)
```


```{r}
length(which(df$pha == "Y"))
p<-ggplot(data=ds, aes(x=pha, y=length(which(pha == "Y")))) + geom_bar(stat="identity")
p
```
Adding to this we also drop id, spkid,  full_name, orbit_id, equinox as they are not necessary.


```{r}
colnames(ds)
ds1 <- ds[-c(1:2, 11, 15)]
print("after removing")
colnames(ds1)
```








